Model for Porous Silicon Structures with a Lateral Gradient

### 2020-11-11 paper.tex
Incorporated Cristian's description of SEM

\subsection{Scanning Electron Microscopy}
\notaL{Insert a paragraph explaining something about how the
  micrographs were obtained. Choose an appropriate title for the
  subsection. Include the definition of the acronym SEM}

>>>>

\subsection{Morphological studies}

The morphology of the etched porous layers (plan-view and
cross-sectional) was observed using (SEM) scanning electron microscopy
(Hitachi SU1510  High Technologies Canada,  Inc., Toronto, Canada).

% the thickness  and porosity  of each fabricated  film was measured.
